Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-08-21 response_to_reviewers.md

# Response to reviewers

## Reviewer 1

> Patrick O'Leary. Review: "Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics". Authorea. July 26, 2019. DOI: [https://doi.org/10.22541/au.156415458.85375575](https://doi.org/10.22541/au.156415458.85375575)
> (CC-BY)

@@

Notes:

* [x] The delete jobs and pool step is missing in figure 1, but presented (including a listing) in the text.
* [x] Do we need to see the content of listing 1 - 4? Why not add a script to the repository and point to it like the YAML config files in examples/snake2d2k35/config_shipyard? 
* [x] The docker build fails on the COPY ../ssh_config stage. Moreover, do the authors want someone to push their image to the authors' docker hub repository? Besides, the repository in footnote 1 contains a typo which highlights the far more significant issues in reproducibility of well-written error-free publications. This paper is a well-written paper, but errors happen.
* [x] The authors generalize that "same container ... can now run at scale." What about the MPI drivers? Does this effect where it can run and what hardware it can use?

**Reply**

* We added the step "Delete jobs and pool" to the workflow in Fig. 1.
* Do we need the listings? — From the reviewer's point of view, these may seem unnecessary, because the reviewer is already an expert in using containers and cloud resources. But we are aiming our paper for readers who are not experts, may have heard of containers as a new and interesting technology, but have never used them. These readers will see from these listings that adopting containers to make their computations more reproducible is not very complicated or time consuming. We want to include these listings as part of the narrative to encourage more researchers to adopt these tools.
* We updated the Dockerfiles to avoid the error message raised during the COPY instruction. We also fixed the typo in the URL of the GitHub repository.
* We do not expect the readers to build the Docker images locally. Indeed, we store the images on DockerHub, so that they can immediately use them. We provide the command-line instructions we used to build the images (as this is part of the workflow). If the readers want to re-build/modify the image locally, we do not expect them to push it to our DockerHub repository. We modified the last paragraph of sub-section 2.1 to reflect our intentions.
* The Docker images were specifically built (on our local workstation) to be able to run MPI applications on RDMA-capable VMs (such as the NC24r instance with a CentOS-based 7.3 HPC image) using multiple-instance tasks on Azure Batch service. The RDMA network on Azure supports MPI traffic for applications running with Intel MPI 5.x (or a later version). (In other words, to take advantage of RDMA on Linux compute nodes, we must use Intel MPI on the nodes.) We added a sentence  over the end of paragraph 4 of the section "Cost Analysis and User Experience" mentioning the Docker image was specifically crafted to be used with Azure Batch service. Thus, we also removed the sentence "same container ... run at scale."

@@

Notes:

* [x] Both the cloud and the six-year old HPC system use FDR Infiniband. Is Azure superior performance a result of tuning, configuration, or age? The analysis provided by this section is that Azure interconnect is improving. Cloud offerings moving from 10 Gbps Ethernet to FDR Infiniband in the past four years makes this result visible without testing. Did we need the OSU benchmarks for verification?
* [x] For the Poisson mini-application, the results again verify Azure has newer hardware than the authors onsite HPC system. However, what was the cause of the variance? Job/Node placement?
* [x] The detailed description of the flying snake workflow is appreciated.

**Reply**

* Is Azure superior performance a result of tuning, configuration, or age? —We didn't apply any manual tuning: both machines are running the same code, but of course the compiler versions are different, and the hardware is different. We are not emphasizing in this paper that performance is "superior" on Azure: just that it is a viable alternative to on-premises HPC clusters (because many researchers continue to be skeptical of cloud). We noticed that the reviewer twice mentions that we're using a "six-year old HPC system." Even if this is an old machine, it is what we have at our university and it is probably the situation for the majority of university researchers that they don't have much choice in regards to the local machines they run on. We certainly are not attempting to do an "apples to oranges" comparison of performance. The point is to dispel the misconception that cloud is (still) inadequate.
* Do we need the OSU benchmark results? We want to showcase that public cloud offerings have improved in the last few years. Our benchmark results show comparable networking performances between our university-managed HPC cluster and Microsoft Azure. We believe it is important to highlight these results as it is still common wisdom that public clouds are inadequate for computational research using HPC. Moreover, Freniere et al. (2016; Computing in Science & Engineering, 18(5), 68) used the same benchmark to compare their local cluster with AWS EC2 and reported performance degradation in networking. With these results, we are updating the readers of CiSE on the improvements of a public cloud such as Microsoft Azure.
* We do not know the cause of the variance in runtime for the Poisson benchmark. However, the benchmark was executed 5 times within a single job task (and thus, on the same physical node), so the variation is not due to Job/Node placement. We have updated the caption of Fig. 3 (Poisson benchmark), detailing the number of MPI processes and the number of GPU devices used per node.

@@

Notes:

* [x] For the user experience, how much did free computing and augmented support from Microsoft influence the authors' determination to utilize this environment. If it cost 20K, would the authors have completed the project?
* [x] Pricing changes every month, every week, maybe every day. Will any of this analysis be relevant by publication?
* [x] Table 5 will be outdated by the time this article is published. It does not add value.
* [x] How does this cost compare to buying a 2 - 8 node equivalent cluster? 
* [x] Singularity containers appear out of the blue in this section with no description.
* [x] The reference for Table 5 in the text is just (5). Is this a cite, a figure, or a listing.

**Reply**

* We would not have attempted this work, were it not for the sponsored cloud credits. We were indeed curious about reproducibility benefits of cloud computing, and that's why we wrote the proposal to Azure Research. But without the sponsorship, we would not have had research budget for this work. In our opinion, this is one of the reasons to publish this paper: other researchers curious about using cloud need this kind of information before they will jump in. With regards to support, we used the standard channels (support tickets and GitHub issues), and it was not "augmented" support. We edited the acknowledgement section, which vaguely used the verb "help," to avoid the impression that we received extra support.
* Price will of course change. We feel it needs to go down. The relevancy of publishing the "snapshot" of today's pricing is precisely as back up that prices should drop. However, the cost of the NC24r instance we used in this study has been 3.96 USD per compute hour for the last two years and it's unlikely that it will change by a lot in the next 6 months.
* Table 5 will be outdated, yes, but it is today's situation, under which we operated. It's also the case that the patterns will continue (i.e., the ratio between the different pricing options).
* Cost compared to buying a cluster? We don't really know. We tried to get some helpful data from our IT department, but were denied the information.
* We added a short description about the Singularity container technology at the end of paragraph 3 of the section "Cost Analysis and User Experience."
* We fixed the reference to Table 5 in the manuscript.

@@

**Changes**

* Properly reference Table 5 of the manuscript ([db21f03](https://github.com/barbagroup/cloud-repro/commit/db21f036e8ae47bb4b6ab61d555a28637542ad1a)).
* Add description about Singularity container technology ([df1e0d5](https://github.com/barbagroup/cloud-repro/commit/df1e0d5f009038b2057a3de8a914662972d80769)).
* * Edit acknowledgements ([9772f42](https://github.com/barbagroup/cloud-repro/commit/9772f42a64d01b4aed7ee497a2f41ff88615cf73)).

@@

---

## Reviewer 2

> Witherden, Freddie (2019): Review of Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics. figshare. Online resource. DOI: [https://doi.org/10.6084/m9.figshare.9159740.v1](https://doi.org/10.6084/m9.figshare.9159740.v1)
> (CC-BY)

### 2019-08-21 response_to_reviewers.md

### Comment 1

* [x] Whilst the manuscript is well written the narrative is somewhat muddled. It starts with an overview of reproducible computational research, then pivots to how containers can be employed within the context of cloud computing, then jumping to benchmarks of one particular cloud providers' hardware, and then -- finally -- pivots a final time to a cost analysis of the public cloud for simulations. These are all interesting topics. Indeed, many a conference proceeding has been dedicated to each of these areas. However, by combining them into a single 10 page document this present manuscript fails to do justice to any of these areas. Further, the high degree of specificity will likely have a negative impact the relevance of the manuscript going forwards; a consequence of it being a review of the current state of affairs of a rapidly evolving field. It would therefore be better if it focused on just one or two areas such as "benchmarking cloud computing platforms" or "reproducibility through containers."

**Reply**

* The main goal of this manuscript is to report how to conduct CFD research in a reproducible way on a public cloud, laying out all the tools we used and the steps we undertook. We intend this paper to also serve as a mini-tutorial for researchers wanting to adopt these reproducible practices (we have observed when giving seminars or domain-conference talks that containers haven't disseminated to the CFD community). We use Docker containers to capture the computational environment and Microsoft Azure tools to capture the run-time environment. The degree of specificity is, in part, the point: precisely reproducing our work presumes deploying the same computational environment.
* Right now, researchers using scientific computing are still concerned about cost and performance on public clouds, and this is why we provide benchmark results and report how much it costs to run our CFD application. Freniere et al. (2016) reported performance degradation on AWS (compared to their local cluster). But in the last three years, cloud providers have improved their offerings for HPC solutions. Thus, another objective is to update the record on the observations made by Freniere et al. (in the same journal) to the new cloud services introduced in the last two years.
* Although cloud computing is a rapidly evolving field, we believe it is important to report on the current state of public cloud offerings for academic applications. 
* The reviewer is a top expert in HPC, and we understand from this point of view it seems the paper does not do justice to the various topics covered. But the intended audience of this paper is not, in fact, either of our reviewers (their expertise was needed, of course, to provide a quality review of the manuscript!). The audience is intended to be researchers using scientific computing (possibly on old and over-subscribed university clusters), who are curious about using cloud resources, and interested in reproducible practices, but need guidelines to adopt these.
* Neither benchmarking cloud computing, nor reproducibility with containers, were a central focus for our paper. We include some benchmark results to update the record with respect to the article by Freniere et al., appearing in the same journal. We use container technology for our reproducible workflow (as others have), but extend the reproducibility ideas to automatic configuration of cloud resources.

@@

### Comment 2

* [x] The manuscript only appears to be concerned with reproducibility in the 'now' and pays no consideration to 'link rot' and if one will be able to build and run the proposed containers in 5, 10, or even 20 years. (C.f. Old F77 codes which are expected to remain viable long after the heat death of the universe.) This is one of the most serious issues affecting reproducible research today. 
* [x] Further, the manuscript also glosses over several of the issues regarding deploying containerised applications within an HPC context. One of the most important is with regards to MPI libraries and the fact that many HPC/Cloud environments depend on specific MPI library. For example, Cray machines require Cray MPI, IBM POWER 9 machines require Spectrum MPI, and so on. This results in a 'leaky abstraction' for the container must now concern itself with the idiosyncrasies of the hardware which it is running on.

**Reply**

* Obsolescence of digital research objects, including software libraries and computational environments, is an acknowledged source of non-reproducibility, in the long run. The recent report of the National Academies highlights it so (page 57). Indeed, tools in our workflow that we have no control over (Azure CLI, Batch Shipyard) will likely change, and perhaps not be backwards compatible. That is inevitable. But when they do, our fully documented workflow (via human-readable configuration files) will continue to offer transparency of what we did and how we did it. 
* "issues regarding deploying containerised applications within an HPC context" — Broad portability of our software and workflow is not our objective, and would (arguably) not be justified. Our software is currently only used in research projects within our lab: what reasons would call for the highly skilled and labor intensive software engineering required to deliver broadly portable software and workflow?The goal is, rather, to publish our computational research with deep transparency. The Docker images built for this study were specifically crafted to run on Microsoft Azure with Azure Batch service on RDMA-capable nodes with Linux-based virtual machines. Readers interested in reproducing our analysis should do it under the same conditions, which include the same cloud environment. We have added text in the introduction explaining the limitations of this work with respect to portability issues.

@@

---

### Comment 3

As highlighted by the authors' in both the manuscript and the Dockerfiles it is necessary (on the Azure platform at least) to use the Intel MPI library. This is highly problematic.

* [x] \(a) It explicitly ties the container to x86 based clusters which support the Intel MPI library (even when the underlying solver software and libraries are portable).
* [x] \(b) The library itself has to be downloaded off a random URL on the Intel website (whose long term stability and availability is suspect).
* [x] \(c) Downloading the library requires acceptance of a proprietary EULA whose terms could easily put an unsuspecting researcher who does not also possess a JD into serious legal trouble with the Intel Corporation -- especially when it comes to moving the container between systems which may be employed for commercial gain. (Aside: whilst in all of the Dockerfiles an rm -rf is performed at the end to remove the Intel components, due to the layered nature of Docker images the compilers are *100%* still present in the resulting images and thus may result in even more legal issues for an unsuspecting researcher.)
* [x] \(d) It is also sub-optimal in the context of CUDA applications for the Intel MPI library is not (to the reviewers' knowledge) CUDA aware and thus parallel CUDA applications are likely to run substantially slower than on say OpenMPI or MVAPICH2 w/GDR.

@@

* Add word "ideally" in the parenthetical note ([56028ea](https://github.com/barbagroup/cloud-repro/commit/56028ead2f917bd5f30f0d781f8d5b253cfb7b07)).

---

### Comment 8

* [x] With regards to the CFD results there does not appear to be any kind of mesh/convergence study nor are any attempts made to quantify the uncertainties on the resulting C\_L and C\_D coefficients. As such it is difficult to know what to make of the results beyond "they look nice." Although the reviewer appreciates the focus of this paper is not the CFD results per-se it is nevertheless important when presenting numerical results to make a case that the method is resolving all relevant dynamics and that any time-averaged statistics are indeed converged.

### 2019-08-22 tex/MesnardoBarba2019.tex
Update legend of Matplotlib figure for forces
The info "(3D)" was missing in the legend.
refine acknowledgements
Fix typo

CFD algorithms often require solving linear systems with iterative methods.
For example, the Navier-Stokes solver implemented in our software requires the solution of a Poisson system at every time step to project the velocity field onto the divergence-free space (to satisfy the incompressibility constraint).
We investigated the time-to-solution for a three-dimensional Poisson system (obtained with a 7-point stencil central-difference scheme) on different nodes of Microsoft Azure and Colonial One.
The solution method was a Conjugate-Gradient (CG) method with a classical algebraic multi-grid (AMG) preconditioner using an exit criterion set to an absolute tolerance of $10^{-12}$.
The iterative solver ran on CPU nodes (\texttt{H16r} instances on Azure and \texttt{Short} nodes on Colonial One) using the CG algorithm from the PETSc library\cite{balay_et_al_2018} and an AMG preconditioner from Hypre BoomerAMG.
Fig. \ref{fig:poisson_benchmarks} (top) reports the mean runtimes (averaged over $5$ repetitions) to iteratively solve the system, on a uniform grid of $50$ million cells ($1000 \times 1000 \times 50$), as we increase the number of nodes in the pool (strong scaling).
Runtimes between obtained on Colonial One and Azure are similar.
We also solved the Poisson system with the NVIDIA AmgX library on multiple GPU devices using \texttt{NC24r} instances on Azure and \texttt{Ivygpu} nodes on Colonial One.
The Poisson system for a base mesh of $6.25$ million cells ($500 \times 500 \times 25$) was solved on a single compute node using $12$ MPI processes and $2$ GPU devices; we then doubled the mesh size as we doubled the number of nodes, keeping the same number of MPI processes and GPUs per node (weak scaling).
The number of iterations to reach convergence increases with the size of the system, so we normalize the runtimes by the number of iterations.
Fig. \ref{fig:poisson_benchmarks} (bottom left) shows the normalized mean runtimes ($5$ repetitions) obtained on Azure and Colonial One.
The smaller runtimes on Azure are explained by the fact that the NC-series of Microsoft Azure features NVIDIA K80 GPU devices with a higher compute capability than the K20 GPUs on Colonial One.
The bottom-right panel of the figure reports the normalized mean runtimes obtained on Azure when we load the bandwidth with a larger problem; the base mesh now contains $25$ millions cells ($1000 \times 500 \times 50$).
We observe larger variations in the time-to-solution for the Poisson system on Microsoft Azure with GPU computing; runtimes are more uniform on Colonial One.

@@

\begin{figure}
    \centering
    \includegraphics[width=8cm]{figures/forceCoefficientsCompare2D.pdf}
    \caption{History of the force coefficients obtained with two- and three-dimensional simulations at Reynolds number $2000$ for a snake cross-section with a $35$-degree angle of attack. As expected, the two-dimensional simulations over-estimate the force coefficients of what is essentially a three-dimensional flow problem.}
    \label{fig:force_coefficients}
\end{figure}

@@

This work was possible thanks to a sponsorship from the Microsoft Azure for Research program\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} and supported by NSF Grant No. CCF-1747669.
We would like to thank Kenji Takeda, Fred Park, and Joshua Poulson of Microsoft for their help.
We are also immensely grateful to the reviewers, Patrick O'Leary \cite{oleary_2019} and Freddie Witherden \cite{witherden_2019}, for their contributions, which helped make the paper's audience and purpose more clear, in addition to other improvements.
We include our detailed replies to the reviewer suggestions as a markdown file in the GitHub repository for this paper (exported from GitHub issues).

>>>>

CFD algorithms often require solving linear systems with iterative methods.
For example, the Navier-Stokes solver implemented in our software requires the solution of a Poisson system at every time step to project the velocity field onto the divergence-free space (to satisfy the incompressibility constraint).
We investigated the time-to-solution for a three-dimensional Poisson system (obtained with a 7-point stencil central-difference scheme) on different nodes of Microsoft Azure and Colonial One.
The solution method was a Conjugate-Gradient (CG) method with a classical algebraic multi-grid (AMG) preconditioner using an exit criterion set to an absolute tolerance of $10^{-12}$.
The iterative solver ran on CPU nodes (\texttt{H16r} instances on Azure and \texttt{Short} nodes on Colonial One) using the CG algorithm from the PETSc library\cite{balay_et_al_2018} and an AMG preconditioner from Hypre BoomerAMG.
Fig. \ref{fig:poisson_benchmarks} (top) reports the mean runtimes (averaged over $5$ repetitions) to iteratively solve the system, on a uniform grid of $50$ million cells ($1000 \times 1000 \times 50$), as we increase the number of nodes in the pool (strong scaling).
Runtimes obtained on Colonial One and Azure are similar.
We also solved the Poisson system with the NVIDIA AmgX library on multiple GPU devices using \texttt{NC24r} instances on Azure and \texttt{Ivygpu} nodes on Colonial One.
The Poisson system for a base mesh of $6.25$ million cells ($500 \times 500 \times 25$) was solved on a single compute node using $12$ MPI processes and $2$ GPU devices; we then doubled the mesh size as we doubled the number of nodes, keeping the same number of MPI processes and GPUs per node (weak scaling).
The number of iterations to reach convergence increases with the size of the system, so we normalize the runtimes by the number of iterations.
Fig. \ref{fig:poisson_benchmarks} (bottom left) shows the normalized mean runtimes ($5$ repetitions) obtained on Azure and Colonial One.
The smaller runtimes on Azure are explained by the fact that the NC-series of Microsoft Azure features NVIDIA K80 GPU devices with a higher compute capability than the K20 GPUs on Colonial One.
The bottom-right panel of the figure reports the normalized mean runtimes obtained on Azure when we load the bandwidth with a larger problem; the base mesh now contains $25$ millions cells ($1000 \times 500 \times 50$).
We observe larger variations in the time-to-solution for the Poisson system on Microsoft Azure with GPU computing; runtimes are more uniform on Colonial One.

@@

\begin{figure}
    \centering
    \includegraphics[width=8.5cm]{figures/forceCoefficientsCompare2D.pdf}
    \caption{History of the force coefficients obtained with two- and three-dimensional simulations at Reynolds number $2000$ for a snake cross-section with a $35$-degree angle of attack. As expected, the two-dimensional simulations over-estimate the force coefficients of what is essentially a three-dimensional flow problem.}
    \label{fig:force_coefficients}
\end{figure}

@@

This work was possible thanks to a sponsorship from the Microsoft Azure for Research program\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} and supported by NSF Grant No. CCF-1747669.
We would like to thank Kenji Takeda, Fred Park, and Joshua Poulson of Microsoft for constructive interactions and listening to our feedback about their products. 
We are also immensely grateful to the reviewers, Patrick O'Leary \cite{oleary_2019} and Freddie Witherden \cite{witherden_2019}, for their contributions, which helped make the paper's audience and purpose more clear, in addition to other improvements.
We include our detailed replies to the reviewer suggestions as a markdown file in the GitHub repository for this paper (exported from GitHub issues).
